%-----------EXPERIENCE-----------%
\section{Experience}
\resumeSubHeadingListStart

    \resumeSubheading
    {Taiwan AI Labs}{Apr 2024 -- Present}
    {Machine Learning Engineer Intern}{Taipei, Taiwan}
    \resumeItemListStart
        \resumeItem{Trained VoiceCraft, a transformer based text-to-speech (TTS) model enabling voice synthesis and editing.}
        \resumeItem{Integrated a customized phonemizer from previous work and a GAN-based vocoder to enhance voice quality.}
		\resumeItem{Enhanced VoiceCraft by integrating VALL-E components, boosting inference performance and quality.}
        \resumeItem{Developed a transformer based lyrics-to-melody model with custom data representation and embedding.}
    \resumeItemListEnd

	\resumeSubheading
    {Institute of Information Science, Academia Sinica}{Jul 2023 -- Apr 2024}
    {Research Assistant}{Taipei, Taiwan}
    \resumeItemListStart
        \resumeItem{Co-authored a paper on service demand extraction using large language models (LLMs), presented at SCC 2024.}
		\resumeItem{Increased input/output extraction accuracy from 56\%/48\% to 97\%/98\%, surpassing previous methods.}
        \resumeItem{Built a custom dataset from LeetCode, enhancing training data quality for service demand extraction tasks.}
        \resumeItem{Optimized prompt design, improving model reasoning accuracy by 15\% through Chain-of-Thought techniques.}
        \resumeItem{Reduced input/output extraction time by 40\%/50\%, significantly improving efficiency.}
    \resumeItemListEnd

\resumeSubHeadingListEnd
