%-----------PROJECTS-----------%
\section{Projects}
\resumeSubHeadingListStart
	\resumeProjectHeading
	{\textbf{ToxicTone} $|$ \emph{Python, PyTorch}}{}
	\resumeItemListStart
		\resumeItem{Co-authored a paper titled ToxicTone as the first author, which was accepted for presentation at Interspeech 2025.}
		\resumeItem{Created the first large-scale Mandarin toxic speech dataset with prosodic labels.}
		\resumeItem{Multimodal models outperformed text-only baselines, highlighting the need for speech-based toxicity detection.}
	\resumeItemListEnd

	\resumeProjectHeading
	{\textbf{Bubblo} $|$ \emph{Unity, C\#}}{}
	\resumeItemListStart
		\resumeItem{Led a team of four engineers and one artist to develop a 2D platformer with unique mechanics and original artwork.}
		\resumeItem{Designed and enforced a modular, low-coupling architecture using object-oriented programming principles.}
		\resumeItem{Adopted agile practices to prioritize tasks, meet deadlines, and iteratively improve gameplay and user experience.}
		\resumeItem{Check out the game here: \href{https://yuxiangluo.itch.io/bubblo}{\underline{Bubblo}}}
	\resumeItemListEnd

	\resumeProjectHeading
	{\textbf{Let's Volley} $|$ \emph{React.js, Nest.js, Node.js, PostgreSQL}}{}
	\resumeItemListStart
		\resumeItem{Built a full-stack web application that connects volleyball players and venue maintainers.}
		\resumeItem{Enabled players to create and join games, and interact with others through a centralized platform.}
		\resumeItem{Allowed maintainers to manage venues, schedule court availability, and oversee game logistics.}
		\resumeItem{Implemented secure authentication with JSON Web Tokens and integrated Google OAuth for easy login.}
		\resumeItem{Utilized Leaflet for interactive venue maps and DayPilot Scheduler for intuitive game and court management.}
	\resumeItemListEnd

	\resumeProjectHeading
	{\textbf{BandWitch} $|$ \emph{Bash, React.js, Express.js, Node.js, Python}}{}
	\resumeItemListStart
		\resumeItem{Developed a monitoring system enabling simultaneous use of multiple networks to scale total bandwidth.}
		\resumeItem{Configured system-level iptables and routing using Bash scripts.}
		\resumeItem{Achieved 80\% scalability in network speed through effective utilization of multiple connections.}
	\resumeItemListEnd

    \resumeProjectHeading
    {\textbf{Machine Problems} $|$ \emph{C, RISCV}}{}
    \resumeItemListStart
		\resumeItem{Implemented user-level threading by allocating separate stacks in heap memory.}
		\resumeItem{Optimized virtual memory management through demand paging and swapping to maximize resource efficiency.}
		\resumeItem{Built xv6’s timer interrupts to enable preemptive user-level threading and designed scheduling algorithms.}
		\resumeItem{Extended the inode structure to support double indirect blocks, increasing the maximum file size in the file system.}
    \resumeItemListEnd

    %\resumeProjectHeading
    %{\textbf{Full Stack Website} $|$ \emph{React.js, Express.js, Node.js, MongoDB}}{}
    %\resumeItemListStart
	%    \resumeItem{Developed a full-stack web application with a responsive front-end and a RESTful API back-end.}
	%    \resumeItem{Implemented user authentication, data management, and CRUD operations with MongoDB as the database.}
	%    \resumeItem{Integrated an auto-recovery mechanism to ensure seamless application restart in case of crashes.}
    %\resumeItemListEnd

\resumeSubHeadingListEnd
